```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      fig.align = "center")
```

```{r load-packages, echo = F}
library(tidyverse)
library(knitr)
library(broom)
library(patchwork)
library(haven)
library(yardstick)
library(naniar)
```

```{r}
Wave1_data <- read_sav("Wave1_20170906.sav")
Wave1_data$index <- 1:nrow(Wave1_data)

predictors <- select(Wave1_data, c(country, level3, se002:se012a, se014:pgnum, index))
```

```{r}
ideology_responses <- Wave1_data %>%
  select(index, q121:q148)
```

```{r}
ideology_responses[is.na(ideology_responses)] <- 100000000
```

```{r}
na_sum <- ideology_responses %>%
  mutate(sum = rowSums(ideology_responses[])) %>%
  filter(sum <499999999)

na_sum[na_sum > 100000] <- NA

na_sum$avg <- rowMeans(subset(na_sum, select = c(q121:q148)), na.rm = TRUE)

average_ideology <- select(na_sum, c(index, avg))
```

```{r}
clean_data <- inner_join(average_ideology, predictors, by = "index")
```

```{r}
gg_miss_var(clean_data)
```

### Mutate predictors

```{r}
final_data <- clean_data %>%
  mutate(country = as.factor(country)) %>%
  mutate(urban_rural = level3 - 1) %>%
  mutate(gender = as.factor(se002 - 1)) %>%
  mutate(age = se003a) %>%
  mutate(marital_status = as.factor(se004a - 1)) %>%
  mutate(education = se005a) %>%
  mutate(household_members = se008a) %>%
  mutate(household_generations = se008b) %>%
  mutate(subjective_status = se017) %>%
  mutate(religion = case_when(se006 == 11 ~ 0, se006 < 11 ~ 1))

levels(final_data$country) <- c("Japan", "Hong Kong", "Korea", "China",
                          "Mongolia", "Philippines", "Taiwan", "Thailand")
```

```{r model}
model <- lm(avg ~ country*gender + gender + education, data = final_data) %>%
  tidy() %>%
  kable(digits = 3)
model
```

Given that zero is not included in any of the countries' confidence intervals, we are 95% confident that the average political index for each country is not the same. We are 95% confident that the political index for males differs from -0.028	to -0.001 compared to females, holding all other predictor variables constant. Also, we are 95% confident that for every additional year in education, the respondant's political index increases by 0.015 to 0.019, holding all other predictor variables constant. 

